\addcontentsline{toc}{section}{Referencias}

\begin{thebibliography}{9}

	\bibitem{antibandwidthGRASP}

	Duarte, A., Martí, R., Resende, M. G., \& Silva, R. M. (2011). \href{https://onlinelibrary.wiley.com/doi/full/10.1002/net.20418}{GRASP with Path Relinking Heuristics for the Antibandwidth Problem }

	\bibitem{hybridMetaheuristicAntibandwith}

	Lozano, M., Duarte, A., Gortázar, F., \& Martí, R. (2013). \href{https://www.sciencedirect.com/science/article/pii/S0950705113002621}{A hybrid metaheuristic for the cyclic antibandwidth problem}

	\bibitem{memeticoAntibandwith}

	Bansal, R., \& Srivastava, K. (2011). \href{https://link.springer.com/article/10.1007/s00500-009-0538-6}{A memetic algorithm for the cyclic antibandwidth maximization problem}

	\bibitem{evolucionDiferencialM2NP}

	Santucci, V., Baioletti, M., Bari, G. D., \& Milani, A. (2019, April). \href{https://link.springer.com/chapter/10.1007/978-3-030-16711-0_2}{A binary algebraic differential evolution for the multidimensional two-way number partitioning problem. In European Conference on Evolutionary Computation in Combinatorial Optimization (Part of EvoStar) (pp. 17-32). Springer, Cham.}

	\bibitem{memeticoM2NP}

	Pop, P. C., \& Matei, O. (2013). \href{https://www.researchgate.net/profile/Oliviu-Matei/publication/299673724_A_Genetic_Algorithm_Approach_for_the_Multidimensional_Two-Way_Number_Partitioning_Problem/links/620df2d5f02286737ca4cd03/A-Genetic-Algorithm-Approach-for-the-Multidimensional-Two-Way-Number-Partitioning-Problem.pdf}{A memetic algorithm approach for solving the multidimensional multi-way number partitioning problem. Applied Mathematical Modelling, 37(22), 9191-9202.}

	\bibitem{programacionLinealM2NP}

	Kojić, J. (2010). \href{https://www.sciencedirect.com/science/article/pii/S0898122110005882}{Integer linear programming model for multidimensional two-way number partitioning problem. Computers & Mathematics with Applications, 60(8), 2302-2308.}

\end{thebibliography}
